%requires packages: moderncv fontawesome

\documentclass[12pt, a4paper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\moderncvicons{awesome} % options awesome / marvosym / letters

\usepackage{fontspec}
\setmainfont{Liberation Sans}[Scale=MatchLowercase]
\setsansfont{DejaVu Sans}[Scale=MatchLowercase]

%\usepackage{inputenc} % character encoding utf8%
%\usepackage{fontenc} % font encoding
%\usepackage{fullpage}
%\usepackage{color}
\usepackage[margin=1.5cm, vmargin=1.5cm]{geometry}

\usepackage{syntonly} %enable when  checking syntax
%\syntaxonly

%\nopagenumbers % remove page number - single page cv
%pagenumber in <c>enter <foot>er
\pagestyle{fancy} % page numbering - set empty to remove
\cfoot{\vspace{-0.3em} \color{color2} \small Resumé --- Arpan Pal: \thepage{} of 2} %\pageref{LastPage}}} %does not work without lastpage.sty specify maximum page

%info
\firstname{Arpan} \lastname{Pal}
\title{ }
\quote{ }
\address{\faHome{} (Omitted}{because this is}{}
\email{arpan.pal010@gmail.com}
\homepage{arpanpal010.github.io}
\phone[mobile]{the Internet)}
\social[github]{arpanpal010}
\social[linkedin]{arpanpal010}
\social[twitter]{arpanpal010}

\AtBeginDocument{\recomputelengths}

\begin{document}
\makecvtitle{}
%
\vspace{-6em} % pull objective up because too much gap
%
%Objective
	\section{Objective}
		\cvline{}{Seeking an opportunity to utilize my skills and abilities in the industry within a \linebreak
					competitive environment along with true professionals, to put in the acquired knowledge and
					gain exposure to upcoming technologies while being resourceful, innovative and flexible.
				}
%
%Skills
	\section{Skills}
		%\cvline
		\cvline{\color{color2}Languages}{Python, Shellscript, Java, HTML$\sim$CSS$\sim$Javascript}
		\cvline{\color{color2}Technologies}{Django, SQLite, MariaDB, Nginx, Uwsgi, Foundation, Git}
		\cvline{\color{color2}Familiar with}{OOP, MVC, \{I \cdotp{} P \cdotp{} S\}aaS, Virtualization, Networking, REST, Responsive Design,
						Amazon EC2 \slash{} EMR \slash{} S3, Boto, Bootstrap, OpenVPN, Mercurial, Heroku, \LaTeX, Markdown
						}
		\cvline{\color{color2}Environment \slash{} IDE}{Vim, Eclipse, NetBeans, Sublime Text 2}
		\cvline{\color{color2}OS}{Several GNU/Linux server and desktop distros \slash{} Windows XP$\sim$7$\sim$8.1 \slash{} OSX \slash{} FreeBSD}
		\vspace{0.6em}
		\cvline{}{Ability to develop and deploy scalable apps in cloud.}
		\cvline{}{Ability to administrate, manage and maintain client-server technologies.}
		\cvline{}{Proficient in Office Suites, and Adobe Photoshop.}
		\cvline{}{Excellent attention to organization and detail as well as time management.}
		\cvline{}{Strong technical, analytical and decision making skills for problem identification and resolution.}
		\cvline{}{Adept at multi-tasking and learning new languages and/or procedures quickly.}
		\cvline{}{Can be a team player as well as work independently/remotely.}
		\cvline{}{Can solve a Rubik's Cube under 01:30 minutes.}
		\cvline{}{Can play the Bass and Acoustic guitar.}
%
%Personal
	\section{Personal}%{Interests}
		\cvline{\color{color1}Interests}{Cloud computing, Operating system architectures, Task and transaction automation, Machine learning,
						Deep learning, Data Mining
					}
		\cvline{\color{color2}Communication}{English, Bengali, Hindi}
%
%Projects
	\section{Projects}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{\link[ArchInst]{https://github.com/arpanpal010/archinst} - Command-line installer (Shellscript) for Arch
						Linux that bootstraps, installs and configures a usable system from scratch with minimum hassle.
					}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{\link[Multi-boot USB]{https://github.com/arpanpal010/mbusb} - Booting multiple (14 as of \today)
						Linux based OS(s) from a single usb key.
					}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{\link[Set-based Similarity Measurement and Ranking Model to Identify Cases of Journalistic Text Reuse]
						{https://arpanpal010.github.io/docs/2013-clinss-Pal-Surrey.pdf} (MSc. Dissertation) secured
						\emph{3rd place} by organization in \link[\underline{C}ross-\underline{L}anguage \underline{!}ndian \underline{N}ews
						\underline{S}tory \underline{S}earch@FIRE'13 task.]
						{http://users.dsic.upv.es/grupos/nle/clinss.html}
					}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{\link[Scalable Non-Obfuscated Plagiarism (Textual) Detection App]
						{https://arpanpal010.github.io/docs/clopladetsys.pdf}
						combining technologies of AmazonEC2, Openstack, and Google App Engine.
					}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{Knowledge based movie ranking engine using Neural Network(Numpy) written in Python2}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{Web Based Student Information Management Interface in Deluge script using Zoho Cloud Creator.}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{Web SMS Gateway using WAMP Server and WayToSMS backend.}
		\cvline{\fontsize{8}{10}\color{lightgray}\faPlus}
					{Prototype of an online banking/accounts management software in JDK6.}
%
%Education
	\section{Education}
%MSc
		\cventry{\color{color1}{2012---13}}{MSc. Internet Computing}{\link[University of Surrey]{http://www.surrey.ac.uk/}}{Guildford, UK}{\textit{64.6\%}}{}
			\vspace{-0.5em}
			\begin{cvcolumns}
				\cvcolumn[0.455555]{\small{Courseworks included \guillemotright}}
					{Cloud Computing (70\%) \\
						Computing Ethics (64\%) \\
						Collective Intelligence (76\%) \\
						Enterprise Systems Development \\
					}
				\cvcolumn{}
					{Database and Knowledge Discovery (71\%) \\
						Web Hacking and Countermeasures (62\%) \\
						Network Technologies and Security (61\%) \\
						Information Security Management \\
					}
			\end{cvcolumns}
%
		\vspace{-1em}
%BCA
		\cventry{\color{color2}{2008---11}}{Bachelor in Computer Application}{\link[The Heritage Academy]{http://www.theheritageacademy.in/}}{Kolkata}{\textit{8.09 (CGPA)}}{}
			\vspace{-0.5em}
			\begin{cvcolumns}
				\cvcolumn[0.32]{\small{Courseworks included \guillemotright}}
					{Computer Architecture \\
						Digital Electronics \\
						Unix Shellscripting \\
						Database Management \\
					}
				\cvcolumn{}
					{Data structure and OOP(Java) \\
						Information System Analysis and Design\\
						Data Communication and Computer Networks \\
						Programming Mathematics and Numerical Algorithms \\
					}
			\end{cvcolumns}
%
		\vspace{-1em}
%School
		\cventry{\color{color2}{2006---08}}{Higher Secondary Examinations (A-Levels Eqv.)}{Krishnapur Adarsha Vidyamandir}{}{\textit{68.4\%}}{}
			\cvline{}{Stream: Science}
			\cventry{\color{color2}{1996---06}}{Secondary Examinations (GCSE Eqv.)}{Krishnapur Adarsha Vidyamandir}{Kolkata}{\textit{79.25\%}}{}
%
	\vspace{2em}
%References
	\hspace{3em}\bfseries{References available on request.}

%PDF version: https://arpanpal010.github.io/docs/cvArpanPal.pdf}
\end{document}
